\section{Procedure}
\label{sec:procedure}

\subsection{Equipment}

\subsection{Procedure}
\subsubsection{Zero Preload}
\begin{enumerate}
    \item Attach the bolted connection to the MTS machine with the nut attached "finger tight" (without a gasket).
    \item Load the bolt 8 times with a range of 0 - 7.5 kN.
    \item Record the external load and bridge imbalance at each load (0, 1, 2, 3, 4, 5, 6, 7, 7.5).
\end{enumerate}
\subsubsection{Repeatability Test}
\begin{enumerate}
    \item Attach the bolt to the MTS machine.
    \item Use the torque wrench to apply a preload of 50 in-lb.
    \item Record the voltage readings from the bolt and washer gauges.
    \item Loosen the bolt to remove any preload.
    \item Repeat steps 2-4 four more times.
\end{enumerate}
\subsubsection{Zero Loading (Torque Test)}
\begin{enumerate}
    \item Attach the bolt to the MTS machine, without a gasket.
    \item Set the external load to 0 kN.
    \item Record the voltage readings from the bolt and washer gauges.
    \item Increase the torque by 25 in-lb.
    \item Record the voltage readings from the bolt and washer gauges.
    \item Repeat steps 4 and 5 four more times, obtaining readings from 0 to 125 in-lb of torque (0, 25, 50, 75, 100, 125).
\end{enumerate}
\subsubsection{Static Loading}
\begin{enumerate}
    \item Attach the bolt to the MTS machine (without a gasket).
    \item Tighten the bolt to 60 in-lb of torque.
    \item Set the external load on the MTS machine to 0 kN.
    \item Set the external load on the MTS machine to 7.5 kN.
    \item Record the readings from the bolt and washer.
    \item Repeat steps 3-5 two more times, totaling three readings (shakedown test).
    \item Leave the bolt assembled, and apply loads ranging from 0-7.5 kN (0, 1, 2, 3, 4, 5, 6, 7, 7.5). Record the output readings from the bolt and washer at each load.
    \item Set the load back to 0 kN.
    \item Disassemble and reassemble the joint with the gasket in place.
    \item Repeat steps 2-9 with a gasket.
\end{enumerate}
\subsubsection{Dynamic Loading}
\begin{enumerate}
    \item Attach the bolt to the MTS machine (without a gasket).
    \item Set the bolt to the "finger tight" torque setting.
    \item Apply an external load of 5 kN and an alternating load of 1.25 kN at 0.3 Hz.
    \item Record data for at least 10 cycles.
    \item Repeat steps 3-4 at different torque settings of 60, 75, and 125 in-lb.
    \item Disassemble and reassemble the joint with the gasket in place.
    \item Repeat steps 2-5 with a gasket.
\end{enumerate}
