\section{Appendix: Shakedown Test Results}
\label{app:shakedown_test}
This section contains the results of the shakedown test. The shakedown test was performed to determine if the bolted connection was subjected to any torsional loading. The shakedown test was performed by ramping the external load from 0 kN to 7.5 kN back down to 0 kN three times in succession. The voltage at the end of each ramp was recorded. The strain transducer reading varied by $\pm 0.005$ V, which was the same magnitude as the resolution of the strain transducer. This indicates that the bolt was not subjected to any torsional loading. The results were consistent with expectations, as the bolt was not subjected to any torsional loading. 


\begin{table}[h]
    \centering
    \caption{Shakedown Test Results}
    \label{tab:shakedown_test}
    \begin{tabular}{cccc}
    \toprule
    & External Load	& Bolt Out & Washer Out \\
    & (kN)	& (V) & (V) \\
    \midrule
    \multirow{3}{*}{Without Gasket} & 0 $\rightarrow$ 7.5 $\rightarrow$ 0 & 0.386 & -0.731 \\
    & 0 $\rightarrow$ 7.5 $\rightarrow$ 0 & 0.382 & -0.720 \\
    & 0 $\rightarrow$ 7.5 $\rightarrow$ 0 & 0.381 & -0.715 \\
    \midrule
    \multirow{3}{*}{With Gasket} & 0 $\rightarrow$ 7.5 $\rightarrow$ 0 & 0.327 & -0.540 \\
    & 0 $\rightarrow$ 7.5 $\rightarrow$ 0 & 0.323 & -0.534 \\
    & 0 $\rightarrow$ 7.5 $\rightarrow$ 0 & 0.321 & -0.530 \\
    \bottomrule
    \end{tabular}
\end{table}

From the results in Table \ref{tab:shakedown_test}, the bolt transducer reading varied by $\pm 0.005$ V, which was the same magnitude as the resolution. This indicates that the bolt was not subjected to any torsional loading. The washer transducer reading varied by $\pm 0.010$ V, which was a magnitude higher than the resolution, but still small relative to the measurement value. This indicates that the washer was not subjected to any torsional loading.