\section{Appendix: Thermistor and Thermocouple Calibration}

\noindent For the thermistor, a linear fit was obtained using Excel's \texttt{LINEST} function. The fit is shown in Figure \ref{fig:thermistor_calibration}
The fit equation is 
\begin{equation}
    T = 331.39 V  -437.46 \label{eq:thermistor_calibration}
\end{equation}

A deviation table was generated using the fit equation to map the thermistor voltage to temperature. The head of the table is shown in 
Table \ref{tab:thermistor_calibration_deviation}. The full table is available in the Excel file submitted with this report.

Deviation was determined by 
\begin{equation}
    \Delta T  = T_{\text{meas}} - T_{\text{ref}} \nonumber
\end{equation}
For the thermistor first measurement at 21.2$^\circ$C, the deviation was
\begin{equation}
    \Delta T = 21.8 - 21.2 = \qty{0.6}{\celsius} \nonumber
\end{equation}

The accuracy of the thermistor was determined by taking the maximum absolute deviation from the reference temperature across all measurements. The 
accuracy was determined to be
\begin{equation}
    Accuracy = \text{max}(|\{\Delta T_{i, j}, \forall i, j\}|) = \qty{2.2}{\celsius} \nonumber
\end{equation}
where $\Delta T_{i, j}$ is the deviation of the $j$th measurement at the $i$th reference temperature.

Repeatability was determined by taking the maximum absolute deviation at each reference temperature. The repeatibility was determined to be
\begin{equation}
    Repeatibility = \text{max}(|\{\Delta T_{j}, \forall j\}|) = \qty{1.0}{\celsius} \nonumber
\end{equation}
where $\Delta T_{j}$ is the maximum deviation of the $i$th reference temperature.

Lastly resolution was determined by
\begin{align*}
    Resolution &= \frac{\Delta V_{\text{fs}}}{2^n \times Sensitivity} \\
               &= \frac{3.3}{2^{10}} \times 331.39 \\
               &= \qty{1.1}{\celsius}
\end{align*}

The accuracy, repeatability, and resolution of the thermocouple were determined in the same manner as the thermistor. The deviation table is shown in
Table \ref{tab:thermocouple_calibration_deviation_adafruit} for the Adafruit conversion equation and Table \ref{tab:thermocouple_calibration_deviation_linear} 
for the linear fit. The fit equation was determined to be
\begin{equation}
    T = 194.56 V - 241.49 \label{eq:thermocouple_calibration}
\end{equation}


